---
title: "DPRPy Assignment No.2"
author: "Onur Caglayan"
output: html_document
---

```{r}
library(xml2)
library(purrr)
library(dplyr)
library(data.table)
```

# Converters
```{r}
BadgesConverter <- function(xmlFilePath){
  #Read the XML file.
  badges_xml <- read_xml(xmlFilePath, useInternalNode = TRUE)
  #Navigate Around The Family Tree.
  data <- xml_children(badges_xml)
  #Apply "xml_attrs" To Each Element Of A Vector.
  data_map <- map(data, xml_attrs)
  #Return data frame.
  Badges_df <- map_df(data_map,~as.list(.))
  
  #Change variables to correct types.
  Badges_df$Id <- as.integer(Badges_df$Id)
  Badges_df$UserId <- as.integer(Badges_df$UserId)
  Badges_df$Date <- as.Date(Badges_df$Date)
  Badges_df$Class <- as.integer(Badges_df$Class)
  return(Badges_df)
}

CommentsConverter <- function(xmlFilePath){
  #Read the XML file.
  comments_xml <- read_xml(xmlFilePath, useInternalNode = TRUE)
  #Navigate Around The Family Tree.
  data <- xml_children(comments_xml)
  #Apply "xml_attrs" To Each Element Of A Vector.
  data_map <- map(data, xml_attrs)
  #Return data frame.
  Comments_df <- map_df(data_map,~as.list(.))
  
  #Change variables to correct types.
  Comments_df$Id <- as.integer(Comments_df$Id)
  Comments_df$PostId <- as.integer(Comments_df$PostId)
  Comments_df$Score <- as.integer(Comments_df$Score)
  Comments_df$CreationDate <- as.Date(Comments_df$CreationDate)
  Comments_df$UserId <- as.integer(Comments_df$UserId)
  return(Comments_df)
}

PostHistoryConverter <- function(xmlFilePath){
  #Read the XML file.
  posthistory_xml <- read_xml(xmlFilePath, useInternalNode = TRUE)
  #Navigate Around The Family Tree.
  data <- xml_children(posthistory_xml)
  #Apply "xml_attrs" To Each Element Of A Vector.
  data_map <- map(data, xml_attrs)
  #Return data frame.
  PostHistory_df <- map_df(data_map,~as.list(.))
  
  #Change variables to correct types.
  PostHistory_df$Id <- as.integer(PostHistory_df$Id)
  PostHistory_df$PostHistoryTypeId <- as.integer(PostHistory_df$PostHistoryTypeId)
  PostHistory_df$PostId <- as.integer(PostHistory_df$PostId)
  PostHistory_df$CreationDate <- as.Date(PostHistory_df$CreationDate)
  PostHistory_df$UserId <- as.integer(PostHistory_df$UserId)
  return(PostHistory_df)
}

PostLinksConverter <- function(xmlFilePath){
  #Read the XML file.
  postlinks_xml <- read_xml(xmlFilePath, useInternalNode = TRUE)
  #Navigate Around The Family Tree.
  data <- xml_children(postlinks_xml)
  #Apply "xml_attrs" To Each Element Of A Vector.
  data_map <- map(data, xml_attrs)
  #Return data frame.
  PostLinks_df <- map_df(data_map,~as.list(.))
  
  #Change variables to correct types.
  PostLinks_df$Id <- as.integer(PostLinks_df$Id)
  PostLinks_df$CreationDate <- as.Date(PostLinks_df$CreationDate)
  PostLinks_df$PostId <- as.integer(PostLinks_df$PostId)
  PostLinks_df$RelatedPostId <- as.integer(PostLinks_df$RelatedPostId)
  PostLinks_df$LinkTypeId <- as.integer(PostLinks_df$LinkTypeId)
  return(PostLinks_df)
}

PostsConverter <- function(xmlFilePath){
  #Read the XML file.
  posts_xml <- read_xml(xmlFilePath, useInternalNode = TRUE)
  #Navigate Around The Family Tree.
  data <- xml_children(posts_xml)
  #Apply "xml_attrs" To Each Element Of A Vector.
  data_map <- map(data, xml_attrs)
  #Return data frame.
  Posts_df <- map_df(data_map,~as.list(.))
  
  #Change variables to correct types.
  Posts_df$Id <- as.integer(Posts_df$Id)
  Posts_df$PostTypeId <- as.integer(Posts_df$PostTypeId)
  Posts_df$AcceptedAnswerId <- as.integer(Posts_df$AcceptedAnswerId)
  Posts_df$ParentId <- as.integer(Posts_df$ParentId)
  Posts_df$CreationDate <- as.Date(Posts_df$CreationDate)
  Posts_df$Score <- as.integer(Posts_df$Score)
  Posts_df$ViewCount <- as.integer(Posts_df$ViewCount)
  Posts_df$OwnerUserId <- as.integer(Posts_df$OwnerUserId)
  Posts_df$LastEditorUserId <- as.integer(Posts_df$LastEditorUserId)
  Posts_df$LastEditDate <- as.Date(Posts_df$LastEditDate)
  Posts_df$LastActivityDate <- as.Date(Posts_df$LastActivityDate)
  Posts_df$AnswerCount <- as.integer(Posts_df$AnswerCount)
  Posts_df$CommentCount <- as.integer(Posts_df$CommentCount)
  Posts_df$FavoriteCount <- as.integer(Posts_df$FavoriteCount)
  Posts_df$ClosedDate <- as.Date(Posts_df$ClosedDate)
  Posts_df$CommunityOwnedDate <- as.Date(Posts_df$CommunityOwnedDate)
  return(Posts_df)
}

TagsConverter <- function(xmlFilePath){
  #Read the XML file.
  tags_xml <- read_xml(xmlFilePath, useInternalNode = TRUE)
  #Navigate Around The Family Tree.
  data <- xml_children(tags_xml)
  #Apply "xml_attrs" To Each Element Of A Vector.
  data_map <- map(data, xml_attrs)
  #Return data frame.
  Tags_df <- map_df(data_map,~as.list(.))
  
  #Change variables to correct types.
  Tags_df$Id <- as.integer(Tags_df$Id)
  Tags_df$Count <- as.integer(Tags_df$Count)
  Tags_df$ExcerptPostId <- as.integer(Tags_df$ExcerptPostId)
  Tags_df$WikiPostId <- as.integer(Tags_df$WikiPostId)
  return(Tags_df)
}

UsersConverter <- function(xmlFilePath){
  #Read the XML file.
  users_xml <- read_xml(xmlFilePath, useInternalNode = TRUE)
  #Navigate Around The Family Tree.
  data <- xml_children(users_xml)
  #Apply "xml_attrs" To Each Element Of A Vector.
  data_map <- map(data, xml_attrs)
  #Return data frame.
  Users_df <- map_df(data_map,~as.list(.))
  
  #Change variables to correct types.
  Users_df$Id <- as.integer(Users_df$Id)
  Users_df$Reputation <- as.integer(Users_df$Reputation)
  Users_df$CreationDate <- as.Date(Users_df$CreationDate)
  Users_df$LastAccessDate <- as.Date(Users_df$LastAccessDate)
  Users_df$Views <- as.integer(Users_df$Views)
  Users_df$UpVotes <- as.integer(Users_df$UpVotes)
  Users_df$DownVotes <- as.integer(Users_df$DownVotes)
  Users_df$AccountId <- as.integer(Users_df$AccountId)
  return(Users_df)
}

VotesConverter <- function(xmlFilePath){
  #Read the XML file.
  votes_xml <- read_xml(xmlFilePath, useInternalNode = TRUE)
  #Navigate Around The Family Tree.
  data <- xml_children(votes_xml)
  #Apply "xml_attrs" To Each Element Of A Vector.
  data_map <- map(data, xml_attrs)
  #Return data frame.
  Votes_df <- map_df(data_map,~as.list(.))
  
  #Change variables to correct types.
  Votes_df$Id <- as.integer(Votes_df$Id)
  Votes_df$PostId <- as.integer(Votes_df$PostId)
  Votes_df$VoteTypeId <- as.integer(Votes_df$VoteTypeId)
  Votes_df$UserId <- as.integer(Votes_df$UserId)
  Votes_df$CreationDate <- as.Date(Votes_df$CreationDate)
  return(Votes_df)
}
```

# Converting "Gamedev" archive
```{r}
Gamedev_Badges <- BadgesConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Gamedev/Badges.xml")
Gamedev_Comments <- CommentsConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Gamedev/Comments.xml")
Gamedev_PostHistory <- PostHistoryConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Gamedev/PostHistory.xml")
Gamedev_PostLinks <- PostLinksConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Gamedev/PostLinks.xml")
Gamedev_Posts <- PostsConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Gamedev/Posts.xml")
Gamedev_Tags <- TagsConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Gamedev/Tags.xml")
Gamedev_Users <- UsersConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Gamedev/Users.xml")
Gamedev_Votes <- VotesConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Gamedev/Votes.xml")
```

# Converting "Bitcoin" archive
```{r}
Bitcoin_Badges <- BadgesConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Bitcoin/Badges.xml")
Bitcoin_Comments <- CommentsConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Bitcoin/Comments.xml")
Bitcoin_PostHistory <- PostHistoryConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Bitcoin/PostHistory.xml")
Bitcoin_PostLinks <- PostLinksConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Bitcoin/PostLinks.xml")
Bitcoin_Posts <- PostsConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Bitcoin/Posts.xml")
Bitcoin_Tags <- TagsConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Bitcoin/Tags.xml")
Bitcoin_Users <- UsersConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Bitcoin/Users.xml")
Bitcoin_Votes <- VotesConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Bitcoin/Votes.xml")
```

# Converting "Ethereum" archive
```{r}
Ethereum_Badges <- BadgesConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Ethereum/Badges.xml")
Ethereum_Comments <- CommentsConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Ethereum/Comments.xml")
Ethereum_PostHistory <- PostHistoryConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Ethereum/PostHistory.xml")
Ethereum_PostLinks <- PostLinksConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Ethereum/PostLinks.xml")
Ethereum_Posts <- PostsConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Ethereum/Posts.xml")
Ethereum_Tags <- TagsConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Ethereum/Tags.xml")
Ethereum_Users <- UsersConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Ethereum/Users.xml")
Ethereum_Votes <- VotesConverter("C:/Users/Onur/Desktop/DPRPY/Datas/Ethereum/Votes.xml")
```

# Description of available Variables (Analysis Part 1)
## Gamedev
### Gamedev Badges
#### Id: Badge ID.
#### UserId: User ID.
#### Name: Name of the Badge.
#### Date: Date of when the achievement was achieved.
#### Class: 1=Gold, 2=Silver and 3=Bronze.
#### TagBased: True if badge is for a tag, otherwise it is a named badge.
```{r}
str(Gamedev_Badges)
```

### Gamedev Comments
#### Id: Id of a specific comment.(It is unqiue for each comment)
#### PostId: Id of a specific post.(Many comments can be for one post)
#### Score: Upvote and Downvote for a specific comment.
#### Text: Text of the comment.
#### CreationDate: Date of the comment.
#### UserId: Id of the author of the comment.
#### ContentLicense: Content License.
#### UserDisplayName: Display name of the user. UserDisplayName=NA means that the user has not changed their default username.
```{r}
str(Gamedev_Comments)
```

### Gamedev PostHistory
#### Id: Primary key.
#### PostHistoryTypeId:
##### 1=Initial Title - initial title(questions only)
##### 2=Initial Body - initial post raw body text
##### 3=Initial Tags - initial list of tags(questions only)
##### 4=Edit Title - modified title(questions only)
##### 5=Edit Body - modified post body(raw markdown)
##### 6=Edit Tags - modified list of tags(questions only)
##### 7=Rollback Title - reverted title(questions only)
##### 8=Rollback Body - reverted body(raw markdown)
##### 9=Rollback Tags - reverted list of tags(questions only)
##### 10=Post Closed - post voted to be closed
##### 11=Post Reopened - post voted to be reopened
##### 12=Post Deleted - post voted to be removed
##### 13=Post Undeleted - post voted to be restored
##### 14=Post Locked - post locked by moderator
##### 15=Post Unlocked - post unlocked by moderator
##### 16=Community Owned - post now community owned
##### 17=Post Migrated - post migrated - now replaced by 35/36(away/here)
##### 18=Question Merged - question merged with deleted question
##### 19=Question Protected - question was protected by a moderator.
##### 20=Question Unprotected - question was unprotected by a moderator.
##### 21=Post Disassociated - OwnerUserId removed from post by admin
##### 22=Question Unmerged - answers/votes restored to previously merged question
##### 24=Suggested Edit Applied
##### 25=Post Tweeted
##### 31=Comment discussion moved to chat
##### 33=Post notice added - comment contains foreign key to PostNotices
##### 34=Post notice removed - comment contains foreign key to PostNotices
##### 35=Post migrated away - replaces id 17
##### 36=Post migrated here - replaces id 17
##### 37=Post merge source
##### 38=Post merge destination
##### 50=Bumped by Community User
##### 52=Question became hot network question(main) / Hot Meta question(meta)
##### 53=Question removed from hot network/meta questions by a moderator
#### PostId: Id of the post.
#### RevisionGUID: At times more than one type of history record can be recorded by a single action. All of these will be grouped using the same RevisionGUID.
#### CreationDate: Creation of the PostHistory.
#### UserId: Id of the user.
#### Text: Text of the Post History.
#### ContentLicense: Content license.
#### Comment: Comment of the post history.
#### UserDisplayName: Display name of the user. UserDisplayName = NA means that the user has not changed their default username.
```{r}
str(Gamedev_PostHistory)
```

### Gamedev PostLinks
#### Id: Primary key.
#### CreationDate: When the link was created.
#### PostId: Id of source post.
#### RelatedPostId: Id of target/related post.
#### LinkTypeId: type of link: 1=Linked(PostId contains a link to RelatedPostId), 3=Duplicate(PostId is a duplicate of RelatedPostId).
```{r}
str(Gamedev_PostLinks)
```

### Gamedev Posts
#### Id: Post Id.
#### PostTypeId: Type of the post. Meanings of Id's:
##### 1=Question
##### 2=Answer
##### 3=Wiki
##### 4=TagWikiExcerpt
##### 5=TagWiki
##### 6=ModeratorNomination
##### 7=WikiPlaceholder
##### 8=PrivilegeWiki.
#### AcceptedAnswerId: Accepted answer id(with a green tick). Only present if PostTypeId=1.
#### CreationDate: Creation date of the post.
#### Score: The score of the post. The number we see between the up and down arrows. It starts at 0. Then other users decide how to rate the post.
#### ViewCount: Number of views of the post. Only present if PostTypeId=1.
#### Body: Post content.
#### OwnerUserId: Id of the user who wrote the post. Only present if user has not been deleted; always -1 for tag wiki entries, for example the community user owns them.
#### LastEditorDisplayName: Name of the last editor.
#### LastEditDate: Date of the last edit.
#### LastActivityDate: Date of the last activity.
#### Title: Content of the title.
#### Tags: Post tags. Only present if PostTypeId=1.
#### AnswerCount: Number of replies to a post/reply.
#### CommentCount: Number of comments to the post.
#### FavoriteCount: Number of favorites
#### ClosedDate: Closing date of the post
#### CommunityOwnedDate: Present only if post is community wiki'd.
#### ContentLicense: Content license.
#### ParentId: The id of the question to which the answer was written. Only present if PostTypeId=2.
#### LastEditorUserId: User Id of the last editor.
#### OwnerDisplayName: Name of the post owner.
```{r}
str(Gamedev_Posts)
```

### Gamedev Tags
#### Id: Primary key.
#### TagName: Tag name. Just a one-word word used as a tag. For example: "path-finding", "tutorials",...
#### Count: Number of uses of a given tag in all posts.
#### ExcerptPostId: Id of Post that holds the excerpt text of the tag.
#### WikiPostId: Id of Post that holds the wiki text of the tag.
```{r}
str(Gamedev_Tags)
```

### Gamedev Users
#### Id: Primary key and User Id.
#### Reputation: When other users vote(UpVote-positive or DownVote-negative) on your posts(Q&A), you generate reputation. The amount of points depends on many factors, but roughly scaled it works like this: sum(UpVote)+sum(downVote)=Reputation
#### CreationDate: User creation date.
#### DisplayName: User nickname.
#### LastAccessDate: When was she/he last logged in.
#### WebsiteUrl: User's website.
#### Location: User's place of residence. Usually in the form of City, State.
#### AboutMe: What the user wrote about himself. Usually a few sentences.
#### Views: Number of times the profile is viewed.
#### UpVotes: UpVote moves content "up" to make it visible to more people.
#### DownVotes: DownVote moves content "down" on the page so fewer people can see it.
#### AccountId: User's Stack Exchange Network profile ID.
#### ProfileImageUrl: URL of profile image.
```{r}
str(Gamedev_Users)
```

### Gamedev Votes
#### Id: Primary key.
#### PostId: Id of the post.
#### VoteTypeId: Vote type:
##### 1=AcceptedByOriginator
##### 2=UpMod(AKA upvote)
##### 3=DownMod(AKA downvote)
##### 4=Offensive
##### 5=Favorite(AKA bookmark; UserId will also be populated)
##### 6=Close(effective 2013-06-25: Close votes are only stored in table: PostHistory)
##### 7=Reopen
##### 8=BountyStart(UserId and BountyAmount will also be populated)
##### 9=BountyClose(BountyAmount will also be populated)
##### 10=Deletion
##### 11=Undeletion
##### 12=Spam
##### 15=ModeratorReview(i.e., a moderator looking at a flagged post)
##### 16=ApproveEditSuggestion
#### CreationDate: Date of the vote. Date only-time data is purposefully removed to protect user privacy.
#### UserId: Present only if VoteTypeId in (5,8); -1 if user is deleted.
#### BountyAmount: Present only if VoteTypeId in (8,9).
```{r}
str(Gamedev_Votes)
```

## Bitcoin
### Bitcoin Badges
#### Id: Badge ID.
#### UserId: User ID.
#### Name: Name of the Badge.
#### Date: Date of when the achievement was achieved.
#### Class: 1=Gold, 2=Silver and 3=Bronze.
#### TagBased: True if badge is for a tag, otherwise it is a named badge.
```{r}
str(Bitcoin_Badges)
```

### Bitcoin Comments
#### Id: Id of a specific comment.(It is unqiue for each comment)
#### PostId: Id of a specific post.(Many comments can be for one post)
#### Score: Upvote and Downvote for a specific comment.
#### Text: Text of the comment.
#### CreationDate: Date of the comment.
#### UserId: Id of the author of the comment.
#### ContentLicense: Content License.
#### UserDisplayName: Display name of the user. UserDisplayName=NA means that the user has not changed their default username.
```{r}
str(Bitcoin_Comments)
```

### Bitcoin PostHistory
#### Id: Primary key.
#### PostHistoryTypeId:
##### 1=Initial Title - initial title(questions only)
##### 2=Initial Body - initial post raw body text
##### 3=Initial Tags - initial list of tags(questions only)
##### 4=Edit Title - modified title(questions only)
##### 5=Edit Body - modified post body(raw markdown)
##### 6=Edit Tags - modified list of tags(questions only)
##### 7=Rollback Title - reverted title(questions only)
##### 8=Rollback Body - reverted body(raw markdown)
##### 9=Rollback Tags - reverted list of tags(questions only)
##### 10=Post Closed - post voted to be closed
##### 11=Post Reopened - post voted to be reopened
##### 12=Post Deleted - post voted to be removed
##### 13=Post Undeleted - post voted to be restored
##### 14=Post Locked - post locked by moderator
##### 15=Post Unlocked - post unlocked by moderator
##### 16=Community Owned - post now community owned
##### 17=Post Migrated - post migrated - now replaced by 35/36(away/here)
##### 18=Question Merged - question merged with deleted question
##### 19=Question Protected - question was protected by a moderator.
##### 20=Question Unprotected - question was unprotected by a moderator.
##### 21=Post Disassociated - OwnerUserId removed from post by admin
##### 22=Question Unmerged - answers/votes restored to previously merged question
##### 24=Suggested Edit Applied
##### 25=Post Tweeted
##### 31=Comment discussion moved to chat
##### 33=Post notice added - comment contains foreign key to PostNotices
##### 34=Post notice removed - comment contains foreign key to PostNotices
##### 35=Post migrated away - replaces id 17
##### 36=Post migrated here - replaces id 17
##### 37=Post merge source
##### 38=Post merge destination
##### 50=Bumped by Community User
##### 52=Question became hot network question(main) / Hot Meta question(meta)
##### 53=Question removed from hot network/meta questions by a moderator
#### PostId: Id of the post.
#### RevisionGUID: At times more than one type of history record can be recorded by a single action. All of these will be grouped using the same RevisionGUID.
#### CreationDate: Creation of the PostHistory.
#### UserId: Id of the user.
#### Text: Text of the Post History.
#### ContentLicense: Content license.
#### Comment: Comment of the post history.
#### UserDisplayName: Display name of the user. UserDisplayName = NA means that the user has not changed their default username.
```{r}
str(Bitcoin_PostHistory)
```

### Bitcoin PostLinks
#### Id: Primary key.
#### CreationDate: When the link was created.
#### PostId: Id of source post.
#### RelatedPostId: Id of target/related post.
#### LinkTypeId: type of link: 1=Linked(PostId contains a link to RelatedPostId), 3=Duplicate(PostId is a duplicate of RelatedPostId).
```{r}
str(Bitcoin_PostLinks)
```

### Bitcoin Posts
#### Id: Post Id.
#### PostTypeId: Type of the post. Meanings of Id's:
##### 1=Question
##### 2=Answer
##### 3=Wiki
##### 4=TagWikiExcerpt
##### 5=TagWiki
##### 6=ModeratorNomination
##### 7=WikiPlaceholder
##### 8=PrivilegeWiki.
#### AcceptedAnswerId: Accepted answer id(with a green tick). Only present if PostTypeId=1.
#### CreationDate: Creation date of the post.
#### Score: The score of the post. The number we see between the up and down arrows. It starts at 0. Then other users decide how to rate the post.
#### ViewCount: Number of views of the post. Only present if PostTypeId=1.
#### Body: Post content.
#### OwnerUserId: Id of the user who wrote the post. Only present if user has not been deleted; always -1 for tag wiki entries, for example the community user owns them.
#### LastEditorDisplayName: Name of the last editor.
#### LastEditDate: Date of the last edit.
#### LastActivityDate: Date of the last activity.
#### Title: Content of the title.
#### Tags: Post tags. Only present if PostTypeId=1.
#### AnswerCount: Number of replies to a post/reply.
#### CommentCount: Number of comments to the post.
#### FavoriteCount: Number of favorites
#### ClosedDate: Closing date of the post
#### CommunityOwnedDate: Present only if post is community wiki'd.
#### ContentLicense: Content license.
#### ParentId: The id of the question to which the answer was written. Only present if PostTypeId=2.
#### LastEditorUserId: User Id of the last editor.
#### OwnerDisplayName: Name of the post owner.
```{r}
str(Bitcoin_Posts)
```

### Bitcoin Tags
#### Id: Primary key.
#### TagName: Tag name. Just a one-word word used as a tag. For example: "path-finding", "tutorials",...
#### Count: Number of uses of a given tag in all posts.
#### ExcerptPostId: Id of Post that holds the excerpt text of the tag.
#### WikiPostId: Id of Post that holds the wiki text of the tag.
```{r}
str(Bitcoin_Tags)
```

### Bitcoin Users
#### Id: Primary key and User Id.
#### Reputation: When other users vote(UpVote-positive or DownVote-negative) on your posts(Q&A), you generate reputation. The amount of points depends on many factors, but roughly scaled it works like this: sum(UpVote)+sum(downVote)=Reputation
#### CreationDate: User creation date.
#### DisplayName: User nickname.
#### LastAccessDate: When was she/he last logged in.
#### WebsiteUrl: User's website.
#### Location: User's place of residence. Usually in the form of City, State.
#### AboutMe: What the user wrote about himself. Usually a few sentences.
#### Views: Number of times the profile is viewed.
#### UpVotes: UpVote moves content "up" to make it visible to more people.
#### DownVotes: DownVote moves content "down" on the page so fewer people can see it.
#### AccountId: User's Stack Exchange Network profile ID.
#### ProfileImageUrl: URL of profile image.
```{r}
str(Bitcoin_Users)
```

### Bitcoin Votes
#### Id: Primary key.
#### PostId: Id of the post.
#### VoteTypeId: Vote type:
##### 1=AcceptedByOriginator
##### 2=UpMod(AKA upvote)
##### 3=DownMod(AKA downvote)
##### 4=Offensive
##### 5=Favorite(AKA bookmark; UserId will also be populated)
##### 6=Close(effective 2013-06-25: Close votes are only stored in table: PostHistory)
##### 7=Reopen
##### 8=BountyStart(UserId and BountyAmount will also be populated)
##### 9=BountyClose(BountyAmount will also be populated)
##### 10=Deletion
##### 11=Undeletion
##### 12=Spam, 15=ModeratorReview(i.e., a moderator looking at a flagged post)
##### 16=ApproveEditSuggestion
#### CreationDate: Date of the vote. Date only-time data is purposefully removed to protect user privacy.
#### UserId: Present only if VoteTypeId in (5,8); -1 if user is deleted.
#### BountyAmount: Present only if VoteTypeId in (8,9).
```{r}
str(Bitcoin_Votes)
```

## Ethereum
### Ethereum Badges
#### Id: Badge ID.
#### UserId: User ID.
#### Name: Name of the Badge.
#### Date: Date of when the achievement was achieved.
#### Class: 1=Gold, 2=Silver and 3=Bronze.
#### TagBased: True if badge is for a tag, otherwise it is a named badge.
```{r}
str(Ethereum_Badges)
```

### Ethereum Comments
#### Id: Id of a specific comment.(It is unqiue for each comment)
#### PostId: Id of a specific post.(Many comments can be for one post)
#### Score: Upvote and Downvote for a specific comment.
#### Text: Text of the comment.
#### CreationDate: Date of the comment.
#### UserId: Id of the author of the comment.
#### ContentLicense: Content License.
#### UserDisplayName: Display name of the user. UserDisplayName=NA means that the user has not changed their default username.
```{r}
str(Ethereum_Comments)
```

### Ethereum PostHistory
#### Id: Primary key.
#### PostHistoryTypeId:
##### 1=Initial Title - initial title(questions only)
##### 2=Initial Body - initial post raw body text
##### 3=Initial Tags - initial list of tags(questions only)
##### 4=Edit Title - modified title(questions only)
##### 5=Edit Body - modified post body(raw markdown)
##### 6=Edit Tags - modified list of tags(questions only)
##### 7=Rollback Title - reverted title(questions only)
##### 8=Rollback Body - reverted body(raw markdown)
##### 9=Rollback Tags - reverted list of tags(questions only)
##### 10=Post Closed - post voted to be closed
##### 11=Post Reopened - post voted to be reopened
##### 12=Post Deleted - post voted to be removed
##### 13=Post Undeleted - post voted to be restored
##### 14=Post Locked - post locked by moderator
##### 15=Post Unlocked - post unlocked by moderator
##### 16=Community Owned - post now community owned
##### 17=Post Migrated - post migrated - now replaced by 35/36(away/here)
##### 18=Question Merged - question merged with deleted question
##### 19=Question Protected - question was protected by a moderator.
##### 20=Question Unprotected - question was unprotected by a moderator.
##### 21=Post Disassociated - OwnerUserId removed from post by admin
##### 22=Question Unmerged - answers/votes restored to previously merged question
##### 24=Suggested Edit Applied
##### 25=Post Tweeted
##### 31=Comment discussion moved to chat
##### 33=Post notice added - comment contains foreign key to PostNotices
##### 34=Post notice removed - comment contains foreign key to PostNotices
##### 35=Post migrated away - replaces id 17
##### 36=Post migrated here - replaces id 17
##### 37=Post merge source
##### 38=Post merge destination
##### 50=Bumped by Community User
##### 52=Question became hot network question(main) / Hot Meta question(meta)
##### 53=Question removed from hot network/meta questions by a moderator
#### PostId: Id of the post.
#### RevisionGUID: At times more than one type of history record can be recorded by a single action. All of these will be grouped using the same RevisionGUID.
#### CreationDate: Creation of the PostHistory.
#### UserId: Id of the user.
#### Text: Text of the Post History.
#### ContentLicense: Content license.
#### Comment: Comment of the post history.
#### UserDisplayName: Display name of the user. UserDisplayName = NA means that the user has not changed their default username.
```{r}
str(Ethereum_PostHistory)
```

### Ethereum PostLinks
#### Id: Primary key.
#### CreationDate: When the link was created.
#### PostId: Id of source post.
#### RelatedPostId: Id of target/related post.
#### LinkTypeId: type of link: 1=Linked(PostId contains a link to RelatedPostId), 3=Duplicate(PostId is a duplicate of RelatedPostId).
```{r}
str(Ethereum_PostLinks)
```

### Ethereum Posts
#### Id: Post Id.
#### PostTypeId:
##### 1=Question
##### 2=Answer
##### 3=Wiki
##### 4=TagWikiExcerpt
##### 5=TagWiki
##### 6=ModeratorNomination
##### 7=WikiPlaceholder
##### 8=PrivilegeWiki.
#### AcceptedAnswerId: Accepted answer id(with a green tick). Only present if PostTypeId=1.
#### CreationDate: Creation date of the post.
#### Score: The score of the post. The number we see between the up and down arrows. It starts at 0. Then other users decide how to rate the post.
#### ViewCount: Number of views of the post. Only present if PostTypeId=1.
#### Body: Post content.
#### OwnerUserId: Id of the user who wrote the post. Only present if user has not been deleted; always -1 for tag wiki entries, for example the community user owns them.
#### LastEditorDisplayName: Name of the last editor.
#### LastEditDate: Date of the last edit.
#### LastActivityDate: Date of the last activity.
#### Title: Content of the title.
#### Tags: Post tags. Only present if PostTypeId=1.
#### AnswerCount: Number of replies to a post/reply.
#### CommentCount: Number of comments to the post.
#### FavoriteCount: Number of favorites
#### ClosedDate: Closing date of the post
#### CommunityOwnedDate: Present only if post is community wiki'd.
#### ContentLicense: Content license.
#### ParentId: The id of the question to which the answer was written. Only present if PostTypeId=2.
#### LastEditorUserId: User Id of the last editor.
#### OwnerDisplayName: Name of the post owner.
```{r}
str(Ethereum_Posts)
```

### Ethereum Tags
#### Id: Primary key.
#### TagName: Tag name. Just a one-word word used as a tag. For example: "path-finding", "tutorials",...
#### Count: Number of uses of a given tag in all posts.
#### ExcerptPostId: Id of Post that holds the excerpt text of the tag.
#### WikiPostId: Id of Post that holds the wiki text of the tag.
```{r}
str(Ethereum_Tags)
```

### Ethereum Users
#### Id: Primary key and User Id.
#### Reputation: When other users vote(UpVote-positive or DownVote-negative) on your posts(Q&A), you generate reputation. The amount of points depends on many factors, but roughly scaled it works like this: sum(UpVote)+sum(downVote)=Reputation
#### CreationDate: User creation date.
#### DisplayName: User nickname.
#### LastAccessDate: When was she/he last logged in.
#### WebsiteUrl: User's website.
#### Location: User's place of residence. Usually in the form of City, State.
#### AboutMe: What the user wrote about himself. Usually a few sentences.
#### Views: Number of times the profile is viewed.
#### UpVotes: UpVote moves content "up" to make it visible to more people.
#### DownVotes: DownVote moves content "down" on the page so fewer people can see it.
#### AccountId: User's Stack Exchange Network profile ID.
#### ProfileImageUrl: URL of profile image.
```{r}
str(Ethereum_Users)
```

### Ethereum Votes
#### Id: Primary key.
#### PostId: Id of the post.
#### VoteTypeId: Vote type:
##### 1=AcceptedByOriginator
##### 2=UpMod(AKA upvote)
##### 3=DownMod(AKA downvote)
##### 4=Offensive
##### 5=Favorite(AKA bookmark; UserId will also be populated)
##### 6=Close(effective 2013-06-25: Close votes are only stored in table: PostHistory)
##### 7=Reopen
##### 8=BountyStart(UserId and BountyAmount will also be populated)
##### 9=BountyClose(BountyAmount will also be populated)
##### 10=Deletion
##### 11=Undeletion
##### 12=Spam
##### 15=ModeratorReview(i.e., a moderator looking at a flagged post)
##### 16=ApproveEditSuggestion
#### CreationDate: Date of the vote. Date only-time data is purposefully removed to protect user privacy.
#### UserId: Present only if VoteTypeId in (5,8); -1 if user is deleted.
#### BountyAmount: Present only if VoteTypeId in (8,9).
```{r}
str(Ethereum_Votes)
```

# Analysis of Part 2 and Part 3
## Summary of "Gamedev"
```{r}
summary(Gamedev_Badges)
summary(Gamedev_Comments)
summary(Gamedev_PostHistory)
summary(Gamedev_PostLinks)
summary(Gamedev_Posts)
summary(Gamedev_Tags)
summary(Gamedev_Users)
summary(Gamedev_Votes)
```

## Summary of "Bitcoin"
```{r}
summary(Bitcoin_Badges)
summary(Bitcoin_Comments)
summary(Bitcoin_PostHistory)
summary(Bitcoin_PostLinks)
summary(Bitcoin_Posts)
summary(Bitcoin_Tags)
summary(Bitcoin_Users)
summary(Bitcoin_Votes)
```

## Summary of Ethereum
```{r}
summary(Ethereum_Badges)
summary(Ethereum_Comments)
summary(Ethereum_PostHistory)
summary(Ethereum_PostLinks)
summary(Ethereum_Posts)
summary(Ethereum_Tags)
summary(Ethereum_Users)
summary(Ethereum_Votes)
```

# Analysis of Part 4
## Top 10 Users of "Gamedev"
```{r}
head(Gamedev_Users[order(-Gamedev_Users$Reputation),],n=10)
```

## Top 10 Users of "Bitcoin"
```{r}
head(Bitcoin_Users[order(-Bitcoin_Users$Reputation),],n=10)
```

## Top 10 Users of "Ethereum"
```{r}
head(Ethereum_Users[order(-Ethereum_Users$Reputation),],n=10)
```

## Top 10 Most Answered Posts from "Gamedev"
```{r}
select(head(Gamedev_Posts[order(-Gamedev_Posts$AnswerCount),],n=10),Title,AnswerCount,CreationDate)
```

## Top 10 Most Answered Posts from "Bitcoin"
```{r}
select(head(Bitcoin_Posts[order(-Bitcoin_Posts$AnswerCount),],n=10),Title,AnswerCount,CreationDate)
```

## Top 10 Most Answered Posts from "Ethereum"
```{r}
select(head(Ethereum_Posts[order(-Ethereum_Posts$AnswerCount),],n=10),Title,AnswerCount,CreationDate)
```

## Number of users from Poland at "Gamedev"
```{r}
GamedevUsers <- Gamedev_Users %>%
filter(grepl("Poland", Location) == TRUE)
nrow(GamedevUsers)
```

## Number of users from Poland at "Bitcoin"
```{r}
BitcoinUsers <- Bitcoin_Users %>%
filter(grepl("Poland", Location) == TRUE)
nrow(BitcoinUsers)
```

## Number of users from Poland at "Ethereum"
```{r}
EthereumUsers <- Ethereum_Users %>%
filter(grepl("Poland", Location) == TRUE)
nrow(EthereumUsers)
```
